Covariate analysis of MAYO reprocessed counts (with TMM normalisation)

### 2017-03-08 code/Rmd/Mayo_RNASeq_Reprocessed_TMM.Rmd

plotdata[grep('CER', plotdata$ID),'Region'] = 'CER'
plotdata[grep('TCX', plotdata$ID),'Region'] = 'TCX'
plotdata$Region = factor(plotdata$Region)
plotdata$Source = factor(plotdata$Source)

>>>>

plotdata[grep('CER', plotdata$ID),'Region'] = 'CER'
plotdata[grep('TCX', plotdata$ID),'Region'] = 'TCX'
plotdata$Region = factor(plotdata$Region)
plotdata$Source = factor(plotdata$Source)
plotdata$ID[!(plotdata$ID %in% c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX"))] = ''
